Formalizing Stack Safety as a Security Property

### 2021-10-01 submission4/main.tex
Messing with figures
Example reorder in text
Merged figures
Fixed alignment

\begin{figure*}
\begin{subfigure}[t]{.2\textwidth}
{\small
  \begin{lstlisting}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y;
  y = *(&y-2);
  *(&y-2) = 0;
  return 5;
}
  \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[t]{.45\textwidth}
  {\small
    \begin{lstlisting}[backgroundcolor=\color{lgray}]
1 main: add $1,%sp      ; allocate frame
2       mov $42,-1(%sp) ; initialize local
3       call f
4       add -1(%sp),%ra ; set return value
5       sub $1,%sp      ; deallocate frame
6       ret

10 f:   add $2,%sp      ; allocate frame
11      mov -4(%sp),-1(%sp) ; violation 1!
12      mov $0,-4(%sp)      ; violation 2!
13      mov $5,%ra      ; set return value
14      sub $1,%sp      ; deallocate frame
15      ret
    \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[t]{.25\textwidth}
\begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\vspace{-4ex}
\end{subfigure}
\caption{Integrity and confidentiality violations
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
    colored backgrounds under the different parts} \sna{I like the minimalism of this, but the code is now set up to support playing with it}\fi}
\vspace*{-1em}
\label{fig:int1}
\end{figure*}

@@

@@

\begin{figure}
\centering
\addtolength{\tabcolsep}{-1em}
\begin{tabular}{l | l}
  \multicolumn{2}{c}{
    2 \hspace{-1.5em}
    \memoryaddrs{8em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \vspace{.5em}
  } \\
  11 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  12 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  \MemoryLabel{-6em}{0.75em}{42}
  \vspace{.5em}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_0\)}
  \vspace{.5em}
\end{tabular}
\addtolength{\tabcolsep}{1em}

\vspace{\abovedisplayskip}

\caption{Noninterference, violated}
\vspace*{-1em}
\label{fig:conf1}
\end{figure}

\begin{figure}
%\begin{center}
\begin{subfigure}[t]{.28\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}
\end{lstlisting}
  }
\end{subfigure}
\begin{subfigure}[t]{.27\columnwidth}
  {\small
\begin{lstlisting}[backgroundcolor=\color{lgray}]
int f() {
  int y = 5;
  return y;
}
\end{lstlisting}
  }
\end{subfigure}
\begin{subfigure}[t]{.32\columnwidth}
  {\small
\begin{lstlisting}
int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\end{subfigure}
\caption{Another confidentiality violation}
\vspace*{-1em}
\label{fig:conf2}
\end{figure}

>>>>

\begin{figure*}
\begin{subfigure}[]{.16\textwidth}
{\small
  \begin{lstlisting}
int main() {
  int x = 42;
  return f()+x;
}

int f() {
  int y;
  y = *(&y-2);
  *(&y-2) = 0;
  return 5;
}
  \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[]{.44\textwidth}
  {\small
    \begin{lstlisting}[backgroundcolor=\color{lgray}]
1 main: add $1,%sp      ;allocate frame
2       mov $42,-1(%sp) ;initialize local
3       call f
4       add -1(%sp),%ra ;set return value
5       sub $1,%sp      ;deallocate frame
6       ret

10 f:   add $1,%sp      ;allocate frame
11      mov -4(%sp),-1(%sp) ;violation 1!
12      mov $0,-4(%sp)      ;violation 2!
13      mov $5,%ra      ;set return value
14      sub $1,%sp      ;deallocate frame
15      ret
    \end{lstlisting}
}
\end{subfigure}
\begin{subfigure}[]{.43\textwidth}
\centering
\addtolength{\tabcolsep}{-1em}
\begin{tabular}{l | l}
  \multicolumn{2}{c}{
    2 \hspace{-1.5em}
    \memoryaddrs{8em}
    \memory{3}{\unsealc}
    ~$\cdots$
    \vspace{.5em}
  } \\
  11 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\unsealc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_1\)}
  \\
  12 \hspace{-1.5em}
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{42}
  \MemoryLabel{-6em}{0.75em}{42}
  \vspace{.5em}
  &
  \memoryaddrs{17em}
  \memory{1}{\unsealc}
  \memory{1}{\retptrc}
  \memory{1}{\badc}
  ~$\cdots$
  \MemoryLabel{-16em}{0.75em}{\(v_0\)}
  \MemoryLabel{-6em}{0.75em}{\(v_0\)}
  \vspace{.5em}
\end{tabular}
\addtolength{\tabcolsep}{1em}
\end{subfigure}
\caption{Integrity and confidentiality violations
\ifaftersubmission\bcp{I wonder if we
    could make the figures easier to read by putting very light, differently
    colored backgrounds under the different parts} \sna{I like the minimalism of this, but the code is now set up to support playing with it}\fi}
\vspace*{-1em}
\label{fig:conf1}
\end{figure*}

@@

\begin{figure}
\begin{subfigure}{.4\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}

int f() {
  int y = 5;
  return y;
}

int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\caption{Leaking through uninitialized data}
\vspace*{-1em}
\label{fig:conf2}
\end{subfigure}
\begin{subfigure}{.5\columnwidth}
  \begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\caption{Integrity Trace}
\label{fig:int1}
\end{subfigure}
\end{figure}

@@
